Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-08 tese2/architecture.tex
[RFT] improving architecture

\chapter{Architecture}
\label{chapter:architecture}
%Esta secção deve englobar:

%\begin{itemize}
%    \item Uma análise de requisitos, onde devem “abrir” portas para as principais
%        características da vossa arquitectura.
%    \item Uma descrição de alto nível da arquitectura do vosso sistema. Esta descrição
%        pode ser:
%        \begin{itemize}
%            \item A arquitectura de rede, explicando os principais componentes e as
%                funções que executam.
%            \item A arquitectura de SW da aplicação, explicando os principais
%                componentes e as funções que executam.
%        \end{itemize}
%    \item Descrições detalhadas de todos os componentes da vossa arquitectura.
%    \item As escolhas que efectuarem em termos de arquitectura global e de detalhe,
%        devem ser justificadas, face aos requisitos que identificaram.
%\end{itemize}

%Sempre que possível, ilustrem a arquitectura com figuras, que descrevam
%sucintamente o modelo como na Figure~\ref{fig:logoCNM}.

%\begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.25\textwidth]{Figures/logoCNM.png}
%  \caption[Caption for figure in TOC]{Caption for figure.}
%  \label{fig:logoCNM}
%\end{figure}

@@

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.4\textwidth]{figures/central.pdf}
	\caption{Centralized Connections}
	\label{fig:central}
	\end{figure}

	In this context, each client must only have one \emph{PeerConnection} to our streaming server and content shown to them is changed on demand either being it an individual or a composite view. This approach is centralized, as seen on figure \ref{fig:central}.

	The same can be applied to instant message delivery, each client must have only one \emph{WebSocket} connection to the application server which consequently relays the messages to other users.

>>>>

\chapter{Architecture}
\label{chapter:architecture}

@@

\begin{figure}[!htb]
\centering
\begin{minipage}[b]{0.45\linewidth}
	\centering
	\includegraphics[width=\textwidth]{figures/ccomposite.pdf}
	\caption{Centralized connections}
	\label{fig:central}
\end{minipage}
\quad
\begin{minipage}[b]{0.45\linewidth}
	\centering
	\includegraphics[width=\textwidth]{figures/dcomposite.pdf}
	\caption{Peer-to-Peer connections}
	\label{fig:p2p}
\end{minipage}
\end{figure}

	In this context, each client must only have one \emph{PeerConnection} to our streaming server and content shown to them is changed on demand either being it an individual or a composite view. This approach is centralized, as seen on figure \ref{fig:central}. Otherwise clients could follow a peer-to-peer connection, as seen on figure \ref{fig:p2p}, which would result on maintaining more connections and performing the composition of videos on client side.

	The composition of streams on client side is performed by receiving streams with the best quality possible but, due to undersizing the video of clients into a smaller region, this would result on wasting bandwidth on a quality that is not needed.

	Although the peer-to-peer approach could be used on our system, we conclude that we need to record the video on our streaming server because web clients have a very limited storage and peer disconnections may result on recorded video loss.

	The same can be concluded to instant message delivery, each client must have only one \emph{WebSocket} connection to the application server which consequently relays the messages to other users.
